A Case Study in Preserving a\\High Energy Physics Application

### 2014-03-19 paper.tex
figure 2 and reference capital problem
modify email of Dr. Hildreth

\title{A Case Study in Preserving a\\High Energy Physics Application}
\author{
Haiyan Meng, Matthias Wolf, Peter Ivie, Anna Woodard, Michael Hildreth, and Douglas Thain\\
\affaddr{Department of Physics and Department of Computer Science and Engineering}\\
\affaddr{University of Notre Dame}\\
\affaddr{\{hmeng|mwolf3|pivie|awoodard|mhildreth|dthain\}@nd.edu}
}
\date{15 January 2014}
\maketitle

@@

In a very abstract sense, reproducing a computation is trivial.
Assuming a computation is deterministic, one must simply
preserve all of the inputs to a computation, then re-run
the same code in an equivalent environment, and the same result
will be produced.  For a small custom application on a modest
amount of data, this could be accomplished by capturing the environment,
data, and software within a single virtual machine image,
and then depositing the virtual
it into a curated environment.  The publication could
then simply refer to the identifier of the image, which the
interested reader can obtain and re-use. This approach has
been used to some success with systems like JVM~\cite{barthe2008preservation}.
\footnote{Of course, we are glossing over the problem that hardware
architectures and virtual machines also change, so one must also
preserve the VMM software necessary to run the image.  The VMM itself
depends on a software environment which must also be preserved.
A long-term preservation system might end up running a whole
stack of nested virtual machines in order to provide the desired
environment! }

>>>>

\title{A Case Study in Preserving a\\High Energy Physics Application}
\author{
Haiyan Meng, Matthias Wolf, Peter Ivie, Anna Woodard, Michael Hildreth, and Douglas Thain\\
\affaddr{Department of Physics and Department of Computer Science and Engineering}\\
\affaddr{University of Notre Dame}\\
\affaddr{\{hmeng|mwolf3|pivie|awoodard|mhildret|dthain\}@nd.edu}
}
\date{15 January 2014}
\maketitle

@@

In a very abstract sense, reproducing a computation is trivial.
Assuming a computation is deterministic, one must simply
preserve all of the inputs to a computation, then re-run
the same code in an equivalent environment, and the same result
will be produced.  For a small custom application on a modest
amount of data, this could be accomplished by capturing the environment,
data, and software within a single virtual machine image,
and then depositing the virtual
it into a curated environment.  The publication could
then simply refer to the identifier of the image, which the
interested reader can obtain and re-use. This approach has
been used to some success with systems mentioned in~\cite{castagne2013consider}.
\footnote{Of course, we are glossing over the problem that hardware
architectures and virtual machines also change, so one must also
preserve the VMM software necessary to run the image.  The VMM itself
depends on a software environment which must also be preserved.
A long-term preservation system might end up running a whole
stack of nested virtual machines in order to provide the desired
environment! }
